
 \documentclass[letterpaper,11pt]{article}
 \usepackage[margin=1in,footskip=0.4in]{geometry}
\usepackage{amsmath,amssymb,amsfonts,mathrsfs,accents} %important math packages
\usepackage{enumerate} % package for making different lists
\usepackage{enumitem}
\usepackage[T1]{fontenc} % Encoding of fonts
\usepackage[utf8]{inputenc} % Encoding of input text
\usepackage[kerning]{microtype} % Better looking text
\usepackage[babel]{csquotes} % Better looking quotes
\usepackage{booktabs} % Better looking tables
\usepackage[american]{babel} % Language control, for hyphenation etc
\usepackage{lmodern}
\usepackage{graphicx} 
\usepackage{float} 
\usepackage{secdot}
\usepackage{mathtools}
\usepackage{placeins}
\usepackage{lscape}
\usepackage{hyperref}
\usepackage[hyphenbreaks]{breakurl}
%\usepackage[hyphens]{url}
\usepackage{scrextend}
\usepackage{parskip}
\setlength\parindent{0pt}
\usepackage{setspace}
\usepackage[gen]{eurosym}

\doublespacing

%\usepackage{subcaption}
\usepackage{chngcntr}
\usepackage{wasysym}
\usepackage[explicit]{titlesec}
\usepackage{multirow}
\usepackage{subcaption}
\usepackage{caption}
\usepackage{bbm}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{docmute} % to skip the preamble in tabout files
\usepackage{epstopdf}
\usepackage{upgreek} %write curly epsilon
\usepackage{bbold} %write indicator 1
%\usepackage[capposition=top]{floatrow}

\usepackage{longtable}
\usepackage{lscape}
\renewcommand{\baselinestretch}{1}

\usepackage[round]{natbib}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Here's where the document begins
%
\begin{document}
\vspace{-0.3cm}
\begin{center}
\begin{huge}
\textbf{Sarah Eichmeyer}
\end{huge} \\
   \begin{normalsize}
\noindent\rule{\textwidth}{1pt}
Department of Economics, Bocconi University, Italy \\
\href{https://sites.google.com/view/saraheichmeyer}{https://sites.google.com/view/saraheichmeyer} \\
sarah.eichmeyer@unibocconi.it \\
\end{normalsize}
\end{center}
   \begin{normalsize}
   
 \medskip

\noindent
{ %\setlength{\extrarowheight}{.5em}

  \begin{tabularx}{\linewidth}{@{}
    >{\raggedright\arraybackslash\hsize=0.15\hsize}X% 10% of 4\hsize 
    >{\raggedright\arraybackslash\hsize=0.85\hsize}X
}
\textbf{Education} & \\
2016-21 & Ph.D. in Economics, Stanford University, U.S.A. \\
&Primary Advisor: Matthew Gentzkow  \\
2014-15 & Graduate coursework, Stockholm University, Sweden  \\
2011-14 & M.Sc. in Economics, University of Zurich, Switzerland  \\
2008-11 & B.A. in Economics, University of Heidelberg, Germany \\
&  \\
\multicolumn{2}{@{} X}{\textbf{Research Interests}} \\
\multicolumn{2}{@{} X}{Public/Health Economics, Political Economy} \\
&  \\
\multicolumn{2}{@{} X}{\textbf{Academic Career and Affiliations}} \\
2022- &  Assistant Professor of Economics, Bocconi University \\
1/2021-2022 & Assistant Professor of Economics, Ludwig Maximilian University of Munich \\
& \\
2022- & Fellow, IGIER and LEAP, Bocconi University \\
2021- & CEPR Research Affiliate (Labour \& Public Economics) \\
2021- & J-PAL North America Invited Researcher (HCDI and SPRI initiatives) \\
2021- & CESifo Research Network Affiliate  \\
&  \\
\multicolumn{2}{@{} X}{\textbf{Honors and Awards}} \\
2023 & Excellence in Refereeing Award, \textit{AER: Insights} \\
2020 & Leonard W. Ely and Shirley R. Ely Graduate Student Fellowship  \\
2019 & Stanford Center on Philanthropy and Civil Society Fellowship \\
2019 & Buckley Memorial Award for best 2nd year paper \\
2010-13    & Scholarship (for B.A. and M.Sc.) from the Foundation of German Business \\
&  \\
\textbf{{Grants}} & \\
2023 & Bocconi University Junior Research Grant (\euro{}10,000) \\
2021 & Thyssen Foundation Grant (\euro{}60,000), with Luca Braghieri \\
2020 & Stanford Computational Social Science Grant (\$10,000), with Christina Kent \\
2018 & VA HSR\&D grant (\$160,000), with Jonathan Zhang \\
& \\
      \end{tabularx}
}

\vspace{-0.4cm} 
\textbf{Publications in Economics}
\medskip

\setlength{\parindent}{0pt}
\setlength{\parskip}{0em}

\begin{itemize}[leftmargin=*]
\itemsep0em 
\item Experimental Evidence on the Effectiveness of Non-Experts for Improving Vaccine Demand (with Marcella Alsan). March 2023. Forthcoming at \textit{American Economic Journal: Economic Policy.}
\item Civil Liberties in Times of Crisis (with Marcella Alsan, Luca Braghieri, Min Jeong Kim, Stefanie Stantcheva and David Yang). July 2022. Forthcoming at \textit{American Economic Journal: Applied Economics.}
\item Primary Care Providers’ Influence on Opioid Use and Its Adverse Consequences (with Jonathan Zhang). \textit{Journal of Public Economics}, Vol. 217, January 2023.
\item Pathways Into Opioid Dependence: Evidence From Practice Variation in Emergency Departments (with Jonathan Zhang). \textit{American Economic Journal: Applied Economics}, Vol. 14(4): 271–300, October 2022.
\item The Welfare Effects of Social Media (with Hunt Allcott, Luca Braghieri and Matthew Gentzkow). \textit{American Economic Review}, Vol. 110, No. 3, March 2020. 
\end{itemize}
\bigskip

\textbf{Publications in Health Policy} 
\medskip
\begin{itemize}[leftmargin=*]
\itemsep0em 
\item Effects of a large-scale social media advertising campaign on holiday travel and COVID-19 infections: a cluster randomized controlled trial (E Breza, F Cody Stanford, M Alsan, B Alsan, A Banerjee, A Chandrasekhar, S Eichmeyer, T Glushko, P Goldsmith-Pinkham, K Holland, E Hoppe, M Karnani, S Liegl, T Loisel, L Ogbu-Nwobodo, B Olken, C Torres, PL Vautrey, E Warner, S Wootton, E Duflo).  \textit{Nature Medicine}, September 2021.
\item Effect of Physician-delivered COVID-19 Public Health Messages and Messages Acknowledging Racial Inequity on Black and White Adults' Knowledge, Beliefs, and Practices Related to COVID-19: A Randomized Clinical Trial (C Torres, L Ogbu-Nwobodo, M Alsan, F Cody Stanford, A Banerjee, E Breza, A Chandrasekhar, S Eichmeyer, M Karnani, T Loisel, P Goldsmith-Pinkham, B Olken, PL Vautrey, E Warner, and E Duflo).   \textit{JAMA Network Open}, July 2021. 
\item Comparison of Knowledge and Information-Seeking Behavior After General COVID-19 Public Health Messages and Messages Tailored for Black and Latinx Communities (M Alsan, F Cody Stanford, A Banerjee, E Breza, A Chandrasekhar, S Eichmeyer, P Goldsmith-Pinkham, L Ogbu-Nwobodo, B Olken, C Torres, A Sankar, PL Vautrey, and E Duflo).  \textit{Annals of Internal Medicine}, April 2021. 
\end{itemize}

\bigskip

\textbf{Working Papers and Work-in-Progress} 
\medskip
\begin{itemize}[leftmargin=*]
\itemsep0em 
\item Parenthood in Poverty (with Christina Kent). CEPR Discussion Paper No. 17722, March 2023.
\item The Value of Learning History (with Luca Braghieri).
\end{itemize}

\bigskip

{
  \begin{tabularx}{\linewidth}{@{}
    >{\raggedright\arraybackslash\hsize=0.15\hsize}X% 10% of 4\hsize 
    >{\raggedright\arraybackslash\hsize=0.85\hsize}X
}
    \multicolumn{2}{@{} X}{\textbf{Invited Seminars and Presentations at Conferences}} \\
    2023 &  CEPR Public Economics Annual Symposium, University College London (UCL), USI Lugano, Stockholm (SOFI), Konstanz, Royal Holloway University of London, Hannover, Tinbergen Institute  \\  
    2022 & CESifo Public Economics Conference, Chicago Harris, Bocconi, Boston University, Essen, Linz, NBER \& MIT Roybal Centers, NBER Trans-Atlantic Public Economics Seminar, USI Lugano, UZH Zurich, Vienna  \\
    2021 & ASSA Annual Meeting, LSE Center for Economic Performance, ifo Institute  \\
      \end{tabularx}
}

\bigskip

{
  \begin{tabularx}{\linewidth}{@{}
    >{\raggedright\arraybackslash\hsize=0.17\hsize}X% 10% of 4\hsize 
    >{\raggedright\arraybackslash\hsize=0.83\hsize}X
}
    \textbf{Refereeing} & \\
     \multicolumn{2}{@{} X}{American Economic Journal: Economic Policy, American Economic Review, American Economic Review: Insights, Econometrica, Economic Journal, European Economic Review, Health Economics, Journal of Economic Behavior \& Organization, Journal of Development Economics, Journal of Health Economics, Journal of Industrial Economics, Journal of Political Economy, Journal of Political Economy: Microeconomics, Management Science, Nature Human Behavior, PLOS One, Review of Economic Studies, Quarterly Journal of Economics, Scandinavian Journal of Economics, Science Advances, Social Science \& Medicine.}
      \end{tabularx}
 }  


\bigskip

{
  \begin{tabularx}{\linewidth}{@{}
    >{\raggedright\arraybackslash\hsize=0.15\hsize}X% 10% of 4\hsize 
    >{\raggedright\arraybackslash\hsize=0.85\hsize}X
}
    \multicolumn{2}{@{} X}{\textbf{Institutional Service and Committee Work}} \\
2023-24 & Bocconi ``Development-Labor-Political Economy'' (DLPE) Seminar Organizer \\
2023 & Expert Reviewer for USAID research grant applications \\
2023 & Program Committee Member for the 2023 European meeting of the Econometric Society (EEA-ESEM) \\
2022-23 & Bocconi Economics Junior Hiring Committee Member \\
2022-23 & Bocconi ``Development-Labor-Political Economy'' (DLPE) Seminar Organizer
      \end{tabularx}
 }  
\bigskip

{
  \begin{tabularx}{\linewidth}{@{}
    >{\raggedright\arraybackslash\hsize=0.15\hsize}X% 10% of 4\hsize 
    >{\raggedright\arraybackslash\hsize=0.85\hsize}X
}
      \multicolumn{2}{@{} X}{\textbf{Teaching}} \\
     2023-24 & Microeconomics, undergraduate (Bocconi University) \\ 
     2022-23 & Microeconomics, undergraduate (Bocconi University) \\ 
     2021-22 & Poverty and Social Mobility, undergraduate (LMU Munich)  \\ 
     2021-22 & Economic and Social Problems: Insights From Big Data, graduate (LMU Munich)  \\ 
     2020-21 & Political Economy and the Media, undergraduate (LMU Munich) \\
2020-21 & CES Lecture on Political Economy and Online Media, graduate (LMU Munich) \\
2018-19 & Teaching Assistant: Behavioral Economics, undergraduate (Stanford University)
      \end{tabularx}
 }  
  
\bigskip
{
  \begin{tabularx}{\linewidth}{@{}
    >{\raggedright\arraybackslash\hsize=0.15\hsize}X% 10% of 4\hsize 
    >{\raggedright\arraybackslash\hsize=0.85\hsize}X
}
      \multicolumn{2}{@{} X}{\textbf{Other Research Experience}} \\
      2013-14 & Research Assistant to Daniel L. Chen, ETH Zurich \\
      2012-13 & Research Assistant to Timo Boppart, University of Zurich \\
      & \\
    \textbf{Languages} & \\
    \multicolumn{2}{@{} X}{German: native. English: fluent. Italian: basic}
      \end{tabularx}
 }  
  
\end{normalsize}

\end{document}
