
 \documentclass[letterpaper,11pt]{article}
 \usepackage[margin=1in,footskip=0.4in]{geometry}
\usepackage{amsmath,amssymb,amsfonts,mathrsfs,accents} %important math packages
\usepackage{enumerate} % package for making different lists
\usepackage[T1]{fontenc} % Encoding of fonts
\usepackage[utf8]{inputenc} % Encoding of input text
\usepackage[kerning]{microtype} % Better looking text
\usepackage[babel]{csquotes} % Better looking quotes
\usepackage{booktabs} % Better looking tables
\usepackage[american]{babel} % Language control, for hyphenation etc
\usepackage{lmodern}
\usepackage{graphicx} 
\usepackage{float} 
\usepackage{secdot}
\usepackage{mathtools}
\usepackage{placeins}
\usepackage{lscape}
\usepackage{hyperref}
\usepackage[hyphenbreaks]{breakurl}
%\usepackage[hyphens]{url}
\usepackage{scrextend}
\usepackage{parskip}
\setlength\parindent{0pt}
\usepackage{setspace}
\usepackage[gen]{eurosym}

\doublespacing

%\usepackage{subcaption}
\usepackage{chngcntr}
\usepackage{wasysym}
\usepackage[explicit]{titlesec}
\usepackage{multirow}
\usepackage{subcaption}
\usepackage{caption}
\usepackage{bbm}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{docmute} % to skip the preamble in tabout files
\usepackage{epstopdf}
\usepackage{upgreek} %write curly epsilon
\usepackage{bbold} %write indicator 1
%\usepackage[capposition=top]{floatrow}

\usepackage{longtable}
\usepackage{lscape}
\renewcommand{\baselinestretch}{1}

\usepackage[round]{natbib}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Here's where the document begins
%
\begin{document}
\vspace{-0.3cm}
\begin{center}
\begin{huge}
\textbf{Sarah Eichmeyer}
\end{huge} \\
   \begin{footnotesize}
\noindent\rule{\textwidth}{1pt}
sarah.eichmeyer@econ.lmu.de \\
\href{https://sites.google.com/view/saraheichmeyer}{https://sites.google.com/view/saraheichmeyer} \\
 +49 (1573) 4890727
\end{footnotesize}
\end{center}
   \begin{footnotesize}

 \medskip

 
 \vspace{-0.4cm}
\noindent
{ %\setlength{\extrarowheight}{.5em}

  \begin{tabularx}{\linewidth}{@{}
    >{\raggedright\arraybackslash\hsize=0.4\hsize}X% 10% of 4\hsize 
    >{\raggedright\arraybackslash\hsize=2.15\hsize}X
    >{\raggedleft\arraybackslash\hsize=0.45\hsize}X
       % sum=3.0\hsize for 3 columns
  }
      \underline {{Position}}  & Assistant Professor of Economics, Ludwig Maximilian University of Munich (Germany) & since 1/2021 \\ 
      & & \\
    \underline {{Education}} & Ph.D. in Economics,  Stanford University (USA) & 2016-1/2021 \\
& Primary Advisor: Matthew Gentzkow & \\
& & \\
& Graduate coursework, Stockholm University (Sweden) & 2014-15 \\
& M.Sc. in Economics, University of Zurich (Switzerland) & 2011-14 \\
& B.A. in Economics, University of Heidelberg (Germany) &  2008-11 \\
& & \\
    \underline {{References}}  & Matthew Gentzkow, Marcella Alsan, Petra Persson &
      \end{tabularx}
 }
 \noindent
{ %\setlength{\extrarowheight}{.5em}

  \begin{tabularx}{\linewidth}{@{}
    >{\raggedright\arraybackslash\hsize=0.266\hsize}X 
    >{\raggedright\arraybackslash\hsize=1.733\hsize}X
       % sum=2.0\hsize for 2 columns
  }
          \underline{Working Papers}  & Parenthood in Poverty (with Christina Kent). November 2021. \\
        & \\
        & Civil Liberties in Time of Crisis (with Marcella Alsan, Luca Braghieri, Min Jeong Kim, Stefanie Stantcheva and David Yang). July 2021. \\
        & \\
& Experimental Evidence on the Effectiveness of Non-Experts for Improving Vaccine Demand (with Marcella Alsan). June 2021. \textit{R\&R at American Economic Journal: Economic Policy.} \\
& \\
        \underline{Recent}   & The Welfare Effects of Social Media (with Hunt Allcott, Luca Braghieri and Matthew Gentzkow). \\ 
        \underline{Publications}  & \textit{American Economic Review}, Vol. 110, No. 3, March 2020.   \\
        &  \\
          & Effects of a large-scale social media advertising campaign on holiday travel and COVID-19 \\
 &  infections: a cluster randomized controlled trial (E Breza, F Cody Stanford, M Alsan, B Alsan, A Banerjee, A Chandrasekhar, S Eichmeyer, T Glushko, P Goldsmith-Pinkham, K Holland, E Hoppe, M Karnani, S Liegl, T Loisel, L Ogbu-Nwobodo, B Olken, C Torres, P-L Vautrey, E Warner, S Wootton, E Duflo).  \textit{Nature Medicine}, August 2021.  \\
         &  \\
        & Pathways Into Opioid Addiction: Evidence From Practice Variation in Emergency Departments. (with Jonathan Zhang). Forthcoming, \textit{American Economic Journal: Applied Economics}.    \\
&
\end{tabularx}
 }

\vspace{-0.5cm}

\noindent
{ %\setlength{\extrarowheight}{.5em}

  \begin{tabularx}{\linewidth}{@{}
    >{\raggedright\arraybackslash\hsize=0.4\hsize}X% 10% of 4\hsize 
    >{\raggedright\arraybackslash\hsize=2.15\hsize}X
    >{\raggedleft\arraybackslash\hsize=0.45\hsize}X
       % sum=3.0\hsize for 3 columns
  }
      \underline {Other} & CEPR Research Affiliate (Labour Economics, Public Economics)  & 2021- \\
      \underline {Affiliations} & J-PAL North America Invited Researcher (HCDI and SPRI initiatives) & 2021- \\
      & & \\
    \underline{{Talks}}  & ASSA Annual Meeting, LSE Center for Economic Performance, ifo Institute, & 2021  \\
    & LMU Munich Econ  & 2020 \\
    & & \\
    \underline {{Grants}}  & Thyssen Foundation Grant (\euro{}60,000), with Luca Braghieri & 2021 \\
    & Stanford Computational Social Science Grant (\$10,000), with Christina Kent. & 2020 \\
    & VA HSR\&D grant (\$160,000), with Jonathan Zhang & 2018-19 \\
    & & \\
    \underline {{Awards}}  & Leonard W. Ely and Shirley R. Ely Graduate Student Fellowship & 2020 \\
    & Stanford Center on Philanthropy and Civil Society Fellowship & 2019-20 \\
    & Buckley Memorial Award for best 2nd year paper & 2019 \\
    & Scholarship (for B.A. and M.Sc.) from the Foundation of German Business & 2010-13 \\
       \end{tabularx}
 }  
  
   \end{footnotesize}

\end{document}
